\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-15 manuscript/main.tex
ridge type formulation

	\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm. This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply doing matrix-vector multiplications

	We now describe the strategy for computing the PLS component direction at the $l$-th iteration. For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
	The goal is to find a unit-norm direction $\xi \in 
	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
	 defined as
\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}}^2 \left( \langle 
	 	\widetilde{W},
	 	\xi \rangle_{\mathcal{H}}, Y \right)
	 	:=
	 	\biggl(
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	\biggr)^2
	 	.
	 \end{equation}
	We denote the maximizer as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})
:= \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 
\left( 
\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
\right)
	\end{equation}
%
	where each functional part $\hat{\xi}_j $  is expressed as
	\begin{equation*}
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
	\end{equation*}

@@

	\begin{proposition}\label{proposition:eigen_noregul}
Let
$
(B^\ast, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, let
$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top$
denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
These coefficients are obtained by solving the following generalized eigenvalue problem:
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi} = 1,
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
\end{equation}

\end{proposition}
Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:linear_noregul}
	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ in Proposition \ref{proposition:eigen_noregul} as 
\begin{equation*}
	\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\zeta}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Proofs of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} are provided in Appendix~\ref{section:proof:proposition:linear_noregul_system_unregularized}.
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
	Although Proposition \ref{proposition:eigen_noregul} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions. Thus, in this section, we provide a modification of Proposition  \ref{proposition:eigen_noregul} that yields regularized (smoothed) PLS components.

	A widely-used approach to smoothing a function $\psi^{(k)}$ is to penalize its roughness that can be quantified by the integrated squared second derivative:
	\begin{equation}
		\textnormal{PEN} \left(\psi^{(k)} \right) 
		=  \int_0^1 \ddot{\psi}^{(k)}(t)^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
		\label{eq: roughness penalty}
	\end{equation}
	where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.

	Now, maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ is not the only aim; we also want to prevent the roughness of each $\psi^{(k)}$---that is, $\textnormal{PEN}(\psi^{(k)})$---from being too large. One possible way to achieve this is to extend \citet{Rice1991}'s approach of obtaining smoothed functional PCA components, and find $\xi^*$ that maximizes:
	\begin{equation}
		\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right) - \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right),
		\label{eq: penalized squred variance}
	\end{equation}
	subject to $\xi^{*\top} J^\ast \xi^*=1$. The equation \eqref{eq: penalized squred variance} quantifies the trade-off between fidelity to the data (in this case the sample covariance between the $\rho=\langle \mathbf{W}, \xi \rangle_\mathcal{H}$ and $Y$ in the direction of $\xi$) and roughness as measured by the sum of the individual penalty terms in \eqref{eq: roughness penalty}. The smoothing parameters $\{\lambda_k\}_{k=1}^K$ control the relative importance between the two objectives. Note that the penalty term can be written concisely using matrices as:
	\begin{equation*}
		\sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
	\end{equation*}
	where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
	\begin{equation}\label{def:Lambda}
		\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
	\end{equation}
	$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

@@

	Define the Lagrangian:
	\[
	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) 
	:= 
	f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
	\]
	The constraint function $g$ is continuously differentiable, and its gradient vanishes only at the origin. Since the origin is not feasible (the constraint requires norm 1), the gradient of $g$ is nonzero at all feasible points. Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
	Taking gradients of $\mathcal{L}$ and setting them to zero yields:
	\begin{align*}
		\nabla_{\mathbf{d}_j} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		B \Theta_j^\top \mathbf{y}
		- 2\lambda B \mathbf{d}_j = 0, \quad \forall j, 
		\numberthis \label{lag_grad_d}
		\\
		\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		Z^\top \mathbf{y}
		- 2\lambda \boldsymbol{\zeta} = 0.
		\numberthis \label{lag_grad_zeta}
	\end{align*}
	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
	$
	\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
	$
	all scaled by the same factor. There exists only one set of vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above. The global maximizer is therefore given by
	\begin{equation*}
		\mathbf{d}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		\Theta_j^\top \mathbf{y},
		\quad
		%%%%%%%%%%%%%%%%
		\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		Z^\top \mathbf{y},
	\end{equation*}
	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
	\end{proof}

>>>>

	\subsubsection{Main estimation strategy}\label{sec: pls component computation intermediate}
	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm. This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply doing matrix-vector multiplications

	We now describe the strategy for computing the PLS component direction at the $l$-th iteration. For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
	The goal is to find a unit-norm direction $\xi \in 
	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
	 defined as
\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}}^2 \left( \langle 
	 	\widetilde{W},
	 	\xi \rangle_{\mathcal{H}}, Y \right)
	 	:=
	 	\biggl(
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	\biggr)^2
	 	.
	 \end{equation}
	We denote the maximizer as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
:= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
\| \xi  \|_\mathcal{H} = 1
 } \widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
\bigr)
	\end{equation}
%
	where each functional part $\hat{\xi}_j $  is expressed as
	\begin{equation*}
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
	\end{equation*}

@@

	\begin{proposition}\label{proposition:eigen_noregul}
Let
$
(B^\ast, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, let
$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top )^\top$
denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
These coefficients are obtained by solving the following generalized eigenvalue problem:
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi} = 1,
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
\end{equation}

\end{proposition}
Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:linear_noregul}
	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
\begin{equation*}
	\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Proofs of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} are provided in Appendix~\ref{section:proof:proposition:linear_noregul_system_unregularized}.
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative $\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt$.
Instead of solely maximizing the squared empirical covariance
 $\widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_\mathcal{H}, Y 
\bigr)
$, 
we incorporate this roughness penalty to simultaneously control the complexity of the estimated functional components.

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
's approach of obtaining smoothed functional PCA components, and find $\xi^*$ that maximizes:
	\begin{equation}
		\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right) - \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right),
		\label{eq: penalized squred variance}
	\end{equation}
	subject to $\xi^{*\top} J^\ast \xi^*=1$. The equation \eqref{eq: penalized squred variance} quantifies the trade-off between fidelity to the data (in this case the sample covariance between the $\rho=\langle \mathbf{W}, \xi \rangle_\mathcal{H}$ and $Y$ in the direction of $\xi$) and roughness as measured by the sum of the individual penalty terms in \eqref{eq: roughness penalty}. The smoothing parameters $\{\lambda_k\}_{k=1}^K$ control the relative importance between the two objectives. Note that the penalty term can be written concisely using matrices as:
		\begin{equation}
		\textnormal{PEN} \left( \hat{\xi}_j \right) 
		=  \int_0^1 
		\bigl\{ \hat{\xi}_j^{''}(t) \bigr\}^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
		\label{eq: roughness penalty}
	\end{equation}
		where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.

	\begin{equation*}
		\sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
	\end{equation*}
	where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
	\begin{equation}\label{def:Lambda}
		\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
	\end{equation}
	$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

@@

	Define the Lagrangian:
	\[
	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) 
	:= 
	f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
	\]
	The constraint function $g$ is continuously differentiable, and its gradient vanishes only at the origin. Since the origin is not feasible (the constraint requires norm 1), the gradient of $g$ is nonzero at all feasible points. Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
	Taking gradients of $\mathcal{L}$ and setting them to zero yields:
	\begin{align*}
		\nabla_{\mathbf{d}_j} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		B \Theta_j^\top \mathbf{y}
		- 2\lambda B \mathbf{d}_j = 0, \quad \forall j, 
		\numberthis \label{lag_grad_d}
		\\
		\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		Z^\top \mathbf{y}
		- 2\lambda \boldsymbol{\zeta} = 0.
		\numberthis \label{lag_grad_zeta}
	\end{align*}
	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
	$
	\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
	$
	all scaled by the same factor. There exists only one set of vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above. The global maximizer is therefore given by
	\begin{equation*}
		\mathbf{d}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		\Theta_j^\top \mathbf{y},
		\quad
		%%%%%%%%%%%%%%%%
		\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		Z^\top \mathbf{y},
	\end{equation*}
	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
	\end{proof}
